Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
added more contributions

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}
\usepackage{epstopdf}

@@

\begin{proof}
Consider the matrix $(A_d - B_d K)$, which updates the states every time step, and select eigenvalue with smallest (non trivial) imaginary value.  
call such value $\vartheta$. 
At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k$ steps we've completed a rotation. 
This is the completeness threshold. 
\end{proof}

@@

%\begin{enumerate}
%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum (\emph{ie} transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}

@@

\begin{proof}
Consider spectrum of matrix $(A_d - B_d K)$ and select eigenvalue with smallest (non trivial) imaginary value.  
call such value $\vartheta$. 
At every time interval $kT_s, (k+1)T_s$ ($T_s$ being the sampling time), 
the dynamics projected on the corresponding eigenspace rotate of $\vartheta T_s$ radiants.  
So surely taking $k$ as the ceiling of $\frac{2\pi}{\vartheta T_s}$, after $k$ steps we've completed a rotation. 
This is the completeness threshold. 
\end{proof}
\item The last {\sc verify} stage, {\sc sampling}, 
ensures that the current sampling rate is large enough by using an 
external checker (\addtodo{add more details here once we have them}).

@@

%\begin{enumerate}
%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
When the abstraction cannot be further refined, and provide them to the {\sc abstract} phase.
\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum (\emph{ie} transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}
